Online supporting information for : \nHunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame

### 2023-02-02 manuscript/Chapter2-SupInfo.Rmd
update supmat

---
title: "Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: e-letters.csl
---

@@

>>>>

---
title: "Online supporting information for : \nHunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: e-letters.csl
---

@@

```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM."}

knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS4.png"))
